``Interestingness'' in Mathematical Theory Exploration

### 2019-06-03 PhDThesis/background_quickcheck.tex
Test quickcheck defs

% BEGIN abs
\begin{haskell}
factorial = original . abs
  where original 0 = 1
        original n = n * naive (n - 1)
\end{haskell}
% END abs

@@

% BEGIN quickchecked
\begin{haskell}
fact_base        = factorial 0 == factorial 1
fact_increases n = factorial n <= factorial (n + 1)
fact_div       n = factorial n == factorial (n + 1) `div` (n + 1)
fact_neg       n = factorial n == factorial (-n)
\end{haskell}
% END quickchecked

>>>>

% BEGIN abs
\begin{haskell}
factorial = original . abs
  where original 0 = 1
        original n = n * original (n - 1)
\end{haskell}
% END abs

@@

% BEGIN quickchecked
\begin{haskell}
fact_base        = factorial 0 == factorial 1

fact_increases, fact_div, fact_neg :: Int -> Bool  
fact_increases n = factorial n <= factorial (n + 1)
fact_div       n = factorial n == factorial (n + 1) `div` (n + 1)
fact_neg       n = factorial n == factorial (-n)
\end{haskell}
% END quickchecked
